\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-07-04 poster.tex
learning from scratch
poster stuff

@@

\begin{block}{Fragment Grammars: Inducing a DSL}
Fragment grammars: first introduced in computational linguistics~\cite{tim}
\begin{figure}[b!]\tabcolsep=2pt
\centering  \begin{minipage}[c]{7.5cm}
  \begin{tikzpicture}[scale=2]
    \node [rotate=90] at (-2.5,-0.5) {prog.};

@@

@@

\begin{column}{\onecolwid} % The second column within column 2 (column 2.2)
\begin{block}{Ongoing work: Generative models for text}
\begin{figure}
\centering
\tiny
\tabcolsep=2pt
\vspace{0pt}
\begin{tabular}{cc}
\begin{tabular}{ccc}
\multicolumn{3}{c}{Tasks:}\\
\hline
cut&F &Moss Side \\ 
control&CL &Burnage \\
control&F & City Centre\\
cut& PCFL& Brooklands \\
\multicolumn{3}{c}{Learned generative models:}\\
\hline
\scode{\textbackslash l*\textbackslash l} & \scode{((\textbackslash
u\textbackslash u)*)\textbar F}& \scode{( \textbar\textbackslash
u\textbackslash w*)*} \\
\multicolumn{3}{c}{Samples from synthesized generative models:}\\
\hline
ya&DQDF & Vr DR \\ 
glrwfdcnc&F &BeF lKQ \\
mgs&F& W\\
piljnl& KI& kqBfZ 0 \\
kj& F& ON\\
zci& GL& Bttc \\
sxpm& F& S \\
\hline
\\
\end{tabular} 
&
\begin{tabular}{c}
\begin{tabular}{l}
\multicolumn{1}{c}{Learned DSL:}\\
\hline
$f_1() = $ \scode{\textbackslash u\textbackslash w*}\\
$f_2(x) = $ \scode{($x$|$f_1$)*} $=$ \scode{($x$|\textbackslash
u\textbackslash w*)*}\\
$f_3(x) = f_2(\scode{space}) = $\scode{( \textbar\textbackslash
u\textbackslash w*)*}\\
\hline
$f_4(x) = $ \scode{($x$*$x$)}\\
\emph{ (equivalent to regex `plus')}\\
$f_5() = f_4(\scode{\textbackslash l}) = \scode{\textbackslash
l*\textbackslash l}$\\
\hline
\end{tabular}
\\
\\
\includegraphics[width=.4\linewidth]{figures/nampiregexjoshcurve3.eps} 
\end{tabular}
\end{tabular}
\vspace{-.3cm}
\caption{regex stuff}
\end{figure}

@@

\begin{block}{Learning from Scratch?}

  \end{block}
\end{column}

>>>>

\usepackage{tikz}
\usetikzlibrary{arrows,shapes}

@@

\begin{block}{Fragment Grammars: Inducing a DSL}
Fragment grammars: introduced in computational linguistics~(O'Donnell~2015)
\begin{figure}[b!]\tabcolsep=2pt
\centering  \begin{minipage}[c]{7.5cm}
  \begin{tikzpicture}[scale=2]
    \node [rotate=90] at (-2.5,-0.5) {prog.};

@@

\begin{block}{Ongoing work: Generative models}
  Learn probabilistic program (a regex) $p_n$ from $K$ strings $x_n = \left\{y_n^k \right\}_{k = 1}^k$.

  Likelihood model:
  $$\probability [x_n|p_n] = \prod_{k = 1}^K \probability[y_n^k|p_n]$$
\begin{figure}
\centering
%\tiny
\tabcolsep=2pt
\vspace{0pt}
\begin{tabular}{cc}
\begin{tabular}{ccc}
\multicolumn{3}{c}{Tasks:}\\
\hline
cut&F &Moss Side \\ 
control&CL &Burnage \\
control&F & City Centre\\
cut& PCFL& Brooklands \\
\multicolumn{3}{c}{Learned generative models:}\\
\hline
\scode{\textbackslash l*\textbackslash l} & \scode{((\textbackslash
u\textbackslash u)*)\textbar F}& \scode{( \textbar\textbackslash
u\textbackslash w*)*} \\
\multicolumn{3}{c}{Samples from synthesized generative models:}\\
\hline
ya&DQDF & Vr DR \\ 
glrwfdcnc&F &BeF lKQ \\
mgs&F& W\\
piljnl& KI& kqBfZ 0 \\
kj& F& ON\\
zci& GL& Bttc \\
sxpm& F& S \\
\hline
\\
\end{tabular} 
&
\begin{tabular}{c}
\begin{tabular}{l}
\multicolumn{1}{c}{Learned DSL:}\\
\hline
$f_1() = $ \scode{\textbackslash u\textbackslash w*}\\
$f_2(x) = $ \scode{($x$|$f_1$)*} $=$ \scode{($x$|\textbackslash
u\textbackslash w*)*}\\
$f_3(x) = f_2(\scode{space}) = $\scode{( \textbar\textbackslash
u\textbackslash w*)*}\\
\hline
$f_4(x) = $ \scode{($x$*$x$)}\\
\emph{ (equivalent to regex `plus')}\\
$f_5() = f_4(\scode{\textbackslash l}) = \scode{\textbackslash
l*\textbackslash l}$\\
\hline
\end{tabular}
\\
\\
\includegraphics[width=.4\linewidth]{figures/nampiregexjoshcurve3.eps} 
\end{tabular}
\end{tabular}
\vspace{-.3cm}
%\caption{regex stuff}
\end{figure}

@@

\begin{column}{\onecolwid} % The second column within column 2 (column 2.2)

\newcommand{\greenCode}[1]{{\footnotesize\popp{\code{#1}}}}
\newcommand{\blueCode}[1]{{\footnotesize\pop{\code{#1}}}}

\begin{block}{Why this works: Bootstrapping}
\begin{figure}\centering
  \begin{tikzpicture}[scale=3]
    \begin{scope}[shift = {(1,-1)}]
    \node[align = center](synthesis) at (6,4) {Search for \\programs: $p$};
    \node[align = center](DSL) at (3,1) {DSL: $\mathcal{D}$};
    \node[align = center](recognitionModel) at (9,1) {Recognition \\model: $Q$};

    \draw [->,thick] (synthesis.-120) to[out = -150,in = 60] node[below,rotate = 45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-G)}} (DSL.30);
    \draw [->,thick] (synthesis.-60) to[out = -30,in = 120] node[below,rotate=-45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-R)}} (recognitionModel.150);
    \draw [->,thick] (DSL.east) to[out = -30,in = 210] node[above, align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-R)}} (recognitionModel.west);

    \draw [->,thick,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white,align = center]{  \footnotesize{Inductive bias}\\\footnotesize{(Wake)}} (synthesis.west);
    \draw [->,thick,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white,align = center]{{\footnotesize Makes tractable}\\{\footnotesize (Wake)}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
 % \caption{\system solves for programs, the DSL, and a recognition model. Each of these steps bootstrap off of the others in a Helmholtz-machine inspired wake/sleep inference algorithm.}  \label{feeding}
\end{figure}

@@

\begin{block}{Learning from Scratch}
  Start w/ McCarthy 1959 Lisp: recursion, conditionals, lists.
  Train on 22 programming exercises.
  After 93 hours on 64 CPUs, rediscovers 9 functional programming staples: \code{map},
  \code{fold}, \code{zip}, \code{unfold}, \code{index}, \code{length}, \code{range}, \code{incr}, \code{decr}.

\end{column}
